---
title: "Roulette Strategy Sim"
output: html_notebook
---

Inspired by a family trip to Las Vegas, I wanted to sim popular betting strategies against betting the same every time or simply randomly increasing or decreasing your bet. In summary, you always have a much larger risk of losing than winng. The D'Alembert strategy has the most upside, but the most risk. Randomly increasing or decreasing your bet actually is a good middle of the road strategy in that you don't as often lose all your money, and have maybe a 20% chance of having more money on hand than what you started with. 


```{r}
library(graphics)
```


set initial parameters
```{r}
#win prob
a = 0.48
#starting money
money_start = 2000
#minimum bet
min_bet = 3
#starting bet amount
bet_start = 5
#bet change by
bet_delta = 4
#interations
iter = 1000
#sessions
session = 1000
```

play the game "standard dalembert"
```{r}
strategy = "dalembert"
maximum_money = c()
minimum_money = c()
rounds_in_green = c()

for(j in 1:session){

Results = Play_Session(min_bet, bet_delta, strategy,a,iter,money_start,bet_start)

maximum_money = cbind(maximum_money,Results[[1]])
minimum_money = cbind(minimum_money,Results[[2]])
rounds_in_green = cbind(rounds_in_green,Results[[3]])
}

print(c("The average maximum money was ",mean(maximum_money),"plus or minus", sd(maximum_money)))
print(c("The average minimum money was ",mean(minimum_money),"plus or minus", sd(minimum_money)))
print(c("The average rounds in green was ",mean(rounds_in_green),"plus or minus", sd(rounds_in_green)))
hist(maximum_money)
hist(minimum_money)
hist(rounds_in_green)

```


play the game "reverse dalembert"
```{r}
strategy = "dalembert_rev"
maximum_money = c()
minimum_money = c()
rounds_in_green = c()

for(j in 1:session){

Results = Play_Session(min_bet, bet_delta, strategy,a,iter,money_start,bet_start)

maximum_money = cbind(maximum_money,Results[[1]])
minimum_money = cbind(minimum_money,Results[[2]])
rounds_in_green = cbind(rounds_in_green,Results[[3]])
}

print(c("The average maximum money was ",mean(maximum_money),"plus or minus", sd(maximum_money)))
print(c("The average minimum money was ",mean(minimum_money),"plus or minus", sd(minimum_money)))
print(c("The average rounds in green was ",mean(rounds_in_green),"plus or minus", sd(rounds_in_green)))
hist(maximum_money)
hist(minimum_money)
hist(rounds_in_green)
```

play the game "constant"
```{r}
strategy = "constant"
maximum_money = c()
minimum_money = c()
rounds_in_green = c()

for(j in 1:session){

Results = Play_Session(min_bet, bet_delta, strategy,a,iter,money_start,bet_start)

maximum_money = cbind(maximum_money,Results[[1]])
minimum_money = cbind(minimum_money,Results[[2]])
rounds_in_green = cbind(rounds_in_green,Results[[3]])
}

print(c("The average maximum money was ",mean(maximum_money),"plus or minus", sd(maximum_money)))
print(c("The average minimum money was ",mean(minimum_money),"plus or minus", sd(minimum_money)))
print(c("The average rounds in green was ",mean(rounds_in_green),"plus or minus", sd(rounds_in_green)))
hist(maximum_money)
hist(minimum_money)
hist(rounds_in_green)
```


play the game "random"
```{r}
strategy = "random"
maximum_money = c()
minimum_money = c()
rounds_in_green = c()

for(j in 1:session){

Results = Play_Session(min_bet, bet_delta, strategy,a,iter,money_start,bet_start)

maximum_money = cbind(maximum_money,Results[[1]])
minimum_money = cbind(minimum_money,Results[[2]])
rounds_in_green = cbind(rounds_in_green,Results[[3]])
}

print(c("The average maximum money was ",mean(maximum_money),"plus or minus", sd(maximum_money)))
print(c("The average minimum money was ",mean(minimum_money),"plus or minus", sd(minimum_money)))
print(c("The average rounds in green was ",mean(rounds_in_green),"plus or minus", sd(rounds_in_green)))
hist(maximum_money)
hist(minimum_money)
hist(rounds_in_green)
```
